The mass distribution of companions to low-mass white dwarfs

### 2014-11-04 documents/letter/ms.tex
Upated .tex

	\tablecomments{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}. $\mathcal{U}$ is the uniform distribution. There are three free parameters. We additionally fix the NS mass distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\

@@

We then applied our model to the set of LMWDs from the ELM WD survey. It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case. Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions. This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}. Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$). Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
%and SDSS J174140.5$+$652638.7 
% and suggest that X-ray and radio follow-up is warranted. We further suggest that the majority of ELM WDs have CO-core WD companions. This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.

>>>>

	\tablecomments{Parameter information for the form of the companion mass distribution used in the tests of Section~\ref{sec:tests}. $\mathcal{U}$ is the uniform distribution. There are three free parameters. We additionally fix the NS mass distribution: $\mu_{\rm NS} = 1.4~\Msun$ and $\sigma_{\rm NS} = 0.05~\Msun.$}\

@@

We then applied our model to the set of LMWDs from the ELM WD survey. It is encouraging that the resulting posterior distribution is qualitatively similar to our two-component Gaussian test case, suggesting that the mass distribution of LMWD companions is well-described by our model. Our model indicates a MAP $\mu_{\rm WD}$ of 0.71 \Msun\ and $\sigma_{\rm WD}$ of 0.26 \Msun, suggesting that a majority of ELM WDs have CO-core WD companions. This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}. Our model further indicates that the fraction of ELM WDs with NS companions is consistent with 0\%, but could be up to $\sim$16\% (within 1-$\sigma$). Finally, our model identifies SDSS J081133.6$+$022556.8 as having the highest median probability of hosting a NS companion.
%and SDSS J174140.5$+$652638.7 
% and suggest that X-ray and radio follow-up is warranted. We further suggest that the majority of ELM WDs have CO-core WD companions. This is in contrast to predictions from population synthesis models which predict the dominant companion population should be He-core WDs \citep[e.g.,][]{toonen12}.
